Electricity Usage in Toronto’s Public Facilities: Analyzing the Impact of Building Size on Energy Consumption

### 2024-09-26 paper/paper.qmd
plot added

library(tidyverse)
library(palmerpenguins)
```

@@

One of the primary determinants of electricity consumption is building size, commonly measured as Gross Floor Area (GFA). Larger buildings tend to consume more energy for lighting, heating, cooling, and equipment operations, but this relationship is influenced by other factors such as building type, operational hours, and energy management systems [@hong2019occupant]. As such, it is crucial for policymakers to understand how building size and other factors influence electricity consumption in Toronto’s public facilities [@li2011managing].

Several studies have shown that energy efficiency measures in public buildings can lead to significant reductions in electricity consumption. For example, retrofitting large government buildings or healthcare facilities with modern energy management systems can reduce energy use, while smaller buildings like libraries and schools often exhibit lower per-square-meter energy consumption [@eto2012impact; @santamouris2016innovative].

@@

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

@@

@@

analysis_data |>
  ggplot(aes(x=log_Area)) +
  geom_histogram(aes(y= ..density..,fill = "pink")) +
  geom_density() +
  ggtitle("Density Plot for Property Area in Toronto")
```

>>>>

#install.packages("opendatatoronto")
#install.packages("tidyverse")
library(tidyverse)
library(palmerpenguins)
```

@@

One of the primary determinants of electricity consumption is building size, commonly measured as Gross Floor Area (GFA). Larger buildings tend to consume more energy for lighting, heating, cooling, and equipment operations, but this relationship is influenced by other factors such as building type, operational hours, and energy management systems [@hong2016occupant]. As such, it is crucial for policymakers to understand how building size and other factors influence electricity consumption in Toronto’s public facilities [@li2009managing].

Several studies have shown that energy efficiency measures in public buildings can lead to significant reductions in electricity consumption. For example, retrofitting large government buildings or healthcare facilities with modern energy management systems can reduce energy use, while smaller buildings like libraries and schools often exhibit lower per-square-meter energy consumption [@scott2008impact].

@@

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()

# Load necessary libraries
library(readxl)
library(ggplot2)
library(tidyverse)

# Relative path, assuming the project root directory is the current working directory
annual_energy_consumption_data_2021 <- readxl::read_excel("~/Desktop/Toronto_annual_energy_consumption/data/raw_data/annual-energy-consumption-data-2021.xlsx", skip = 5)

# Select and mutate columns, assigning the result back to the original data
annual_energy_consumption_data_2021 <- annual_energy_consumption_data_2021 |>
  dplyr::select(`Property GFA - Self-Reported (m²)`, `Electricity Use - Grid Purchase (kWh)`,  `City`) |>
  dplyr::mutate(Area = `Property GFA - Self-Reported (m²)`,
                kWh = `Electricity Use - Grid Purchase (kWh)`,
                City = `City`)  # Ensure City is the correct column name without quotes

# 基于数据的分面调整，并移除不必要的元素
annual_energy_consumption_data_2021 %>%
  ggplot(aes(x = Area, y = kWh, color = City)) +
  geom_point(alpha = 0.5) + # 设置透明度以减少重叠的影响
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~ City, scales = "free") + # 允许每个分面自由缩放，以适应各自的范围
  ggtitle("Electricity Usage vs Building Size by Facility Type") +
  xlab("Building Size (GFA in m²)") +
  ylab("Electricity Usage (kWh)") +
  theme_minimal() +
  theme(
    axis.text.y = element_blank(),  # 去掉y轴的数字
    axis.ticks.y = element_blank(),  # 去掉y轴的刻度
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

# Load necessary libraries
library(readxl)
library(ggplot2)
library(dplyr)

# Read the data from Excel
annual_energy_consumption_data_2021 <- readxl::read_excel("~/Desktop/Toronto_annual_energy_consumption/data/raw_data/annual-energy-consumption-data-2021.xlsx", skip = 5)

# Reclassify 'Other' types into a single 'Other' category
annual_energy_consumption_data_2021 <- annual_energy_consumption_data_2021 %>%
  mutate(Property_Type = case_when(
    grepl("Other", `Primary Property Type - Self Selected`) ~ "Other",
    TRUE ~ `Primary Property Type - Self Selected`
  ))

# Plotting the data
ggplot(annual_energy_consumption_data_2021, aes(x = `Property GFA - Self-Reported (m²)`, y = `Electricity Use - Grid Purchase (kWh)`, color = Property_Type)) +
  geom_point(alpha = 0.5) + # Set transparency to avoid overlapping
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~ Property_Type, scales = "free") + # Facet based on Property_Type
  ggtitle("Electricity Usage vs Building Size by Facility Type") +
  xlab("Building Size (GFA in m²)") +
  ylab("Electricity Usage (kWh)") +
  theme_minimal() +
  theme(
    axis.text.y = element_blank(), # Remove y-axis numbers
    axis.ticks.y = element_blank(), # Remove y-axis ticks
    axis.text.x = element_text(angle = 45, hjust = 1) # Rotate x-axis text
  )

@@

library(ggplot2)

@@

analysis_data |>
  ggplot(aes(x=log_Area)) +
  geom_histogram(aes(y= ..density..,fill = "pink")) +
  geom_density() +
  ggtitle("Density Plot for Property Area in Toronto")

```{r}
#| label: second
#| fig-cap: Relationship between ...
#| echo: false
#| message: false
#| warning: false

# Filter out zero or negative values (if needed)

analysis_data <- analysis_data |> 
  dplyr::filter(kWh > 0)

# Plot the histogram and density
analysis_data |>
  ggplot(aes(x = kWh)) +
  geom_histogram(aes(y = ..density..), fill = "orange", binwidth = 250000) +  # Adjust bin width
  geom_density() +
  ggtitle("Density Plot for Electricity Use in Toronto") +
  theme_minimal()
